Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2025-03-03 paper/1_Initial/manuscript.qmd
minor

<!-- ICQ -->
The Interoceptive Confusion Questionnaire (ICQ; @brewer2016alexithymia) was used to assess individuals' difficulties in interpreting non-affective physiological states, such as pain and hunger. The ICQ consists of 20 items rated on a scale from 1 ("Does not describe me") to 5 ("Describes me very well"), with higher scores indicating greater interoceptive confusion.

@@

Mood disorders were assessed using several standardized measures, including the General Anxiety Disorder-2 [GAD-2; @kroenke2007anxiety], the State-Trait Anxiety Inventory [STAI; @spielberger1970manual] and its shorter version, the STAI-5 [@zsido2020development], Beck’s Depression Inventory [BDI; @beck1996beck], and the Mood and Feelings Questionnaire [MFQ; @messer1995development].
Additionally, the Patient Health Questionnaire (PHQ) was administered in its 2-item [PHQ-2; @kroenke2003patient], 9-item [PHQ-9; @kroenke2001phq], and 15-item [PHQ-15; @kroenke2002phq] versions.
Finally, borderline personality traits were assessed using the McLean Screening Instrument for Borderline Personality Disorder [MSI-BPD; @zanarini2003zanarini].

>>>>

<!-- ICQ -->
The Interoceptive Confusion Questionnaire was used to assess individuals' difficulties in interpreting non-affective physiological states, such as pain and hunger. The ICQ consists of 20 items rated on a scale from 1 ("Does not describe me") to 5 ("Describes me very well"), with higher scores indicating greater interoceptive confusion.

@@

Mood disorders were assessed using several standardized measures, including the General Anxiety Disorder-2 [GAD-2, @kroenke2007anxiety], the State-Trait Anxiety Inventory [STAI, @spielberger1970manual] and its shorter version, the STAI-5 [@zsido2020development], Beck’s Depression Inventory [BDI, @beck1996beck], and the Mood and Feelings Questionnaire [MFQ; @messer1995development].
Additionally, the Patient Health Questionnaire (PHQ) was administered in its 2-item [PHQ-2; @kroenke2003patient], 9-item [PHQ-9; @kroenke2001phq], and 15-item [PHQ-15, @kroenke2002phq] versions.
Finally, borderline personality traits were assessed using the McLean Screening Instrument for Borderline Personality Disorder [MSI-BPD; @zanarini2003zanarini].
